Comparative Analysis of Legislative Complex Networks of Select North American and European Countries

### 2018-12-09 paper/paper.tex
moved repository link to authors
updating paper

\begin{abstract}
    Given the complex nature of today's political climate, we were interested in analyzing and quantifying various legislative bodies in select first-world countries. To do so, we performed complex network analysis on North Amerian and European countries to understand how a wide variety political parties interacted with respect to cosponshorship. 
\end{abstract}

@@

\newpage

>>>>

\begin{abstract}
    Given the complex nature of today's political climate, we were interested in analyzing and quantifying various legislative bodies in select first-world countries. To do so, we performed complex network analysis on North Amerian and European countries to understand how a wide variety political parties interacted amongst each other with respect to cosponshorship. 
    % To-do: Finish abstract %
\end{abstract}

@@

\section{Methods}
\subsection{Data Collection}
Cosponsorship data was taken from the following resources: \underline{Bill cosponshorship network} \cite{briatte}, \underline{Cosponsorship Network} \cite{fowler}, \underline{UK Parliament} \cite{UK}, and \underline{United States Congress} \cite{US}.

\section{Results}

\section{Discussion}

\newpage
\begin{thebibliography}{9}

\bibitem{briatte} Briatte, Francois. 2016. ``Bill cosponsorship networks in European parliaments.'' \url{https://github.com/briatte/parlnet}.

\bibitem{fowler} Fowler, J. H., Waugh, A.S., and Sohn, Y. 2010. ``Cosponsorship Network.'' \url{http://jhfowler.ucsd.edu/cosponsorship.htm}

\bibitem{UK} UK Parliament. \url{https://edm.parliament.uk/}

\bibitem{US} United States Congress. \url{https://github.com/unitedstates/congress}
\end{thebibliography}
